---
title: "Testing regression functions"
author: "Christopher Huebel"
date: "2023-06-20"
output:
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Clear Global Environment
```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```

Load packages

```{r Load packages}
library(flextable)
library(officer)
library(gtsummary)
library(tidyverse)
```

Set current date

```{r current date}
date <- Sys.Date()
```

Load data

```{r Load data}
dat <- read_rds(
  file =
    paste0(filepath_cleaned_data,"dat_after_exclusion", date, ".rds")
)
```


```{r}
dat %>% names
```

# Linear example

Psychiatric diagnoses
```{r Psychiatric diagnoses vector}
psy_dx_factors <- c(
  "mhd.personality_disorder",
  "mhd.mdd",
  "mhd.gad",
  "mhd.ptsd",
  "mhd.ocd",
  "mhd.bdd",
  "mhd.an",
  "mhd.atypical_an",
  "mhd.bn",
  "mhd.bed"
)
```


```{r}
model0_adjustment <- c(
  "gender",
  "age",
  "sexual_orientation",
  "ethnicity"
)
model0_adjustment

model1_adjustment <- c(
  model0_adjustment,
  "bmi",
  "height_m"
)
model1_adjustment

model2_adjustment <- c(
  model0_adjustment,
  "bmi",
  "height_m"
)
model2_adjustment

model3_adjustment <- c(
  model0_adjustment,
  "dem.highest_education_collapsed"
)
model3_adjustment

model4_adjustment <- c(
  model0_adjustment,
  psy_dx_factors
)

model4_adjustment
```


```{r}
bddtrauma_linear <-
  linear.estimates(
    outcome = "dcq.sum_score",
    explanatory_variables = c(
      "cts.any_maltreatment_binary",
      "ats.adult_trauma_binary"),
    adjustment = model1_adjustment,
    population = "Full sample",
    data_set = "dat")

bddtrauma_linear
```


```{r}
bddtrauma_linear_statistics <-
  linear.estimates(
    outcome = "dcq.sum_score",
    explanatory_variables = "gender",
    population = "Full sample",
    data_set = "dat")

bddtrauma_linear_statistics
```